Named Entity Recognition using Structured Prediction

### 2012-11-03 doc/report/paper.tex
paper++

@@

\section{Introduction}
Named Entity Recognition (NER) is an information extraction task and has first been introduced as part of the 6th MUC (Sixth Message Understanding Conference)
that was focusing on the extraction of structured information from unstructured text, such as company names from newspaper articles \cite{ner-sekine2007}.
The most prominent types are generally known under the name of \emph{enamex} types, which are comprised of \texttt{Person Names}, \texttt{Organisations} and \texttt{Locations}. 
An additional type \texttt{Miscellaneous} captures person names outside the classic \emph{enamax} type.
Apart from these there is \emph{timex}, which covers date \& time expressions and \emph{numex} which is for monetary values \& percent. 
Table \ref{NETypes} gives an overview of the different NE types.

\begin{table}[h!]
\scriptsize
\begin{tabular}{l|l}
\hline
\bf Named Entity Type & \bf Example \\
\hline
Person Names & Greta Garbo, John, Mary \\
Organisations& Benetton, Coca-Cola Gmbh\\
Locations&  Paris, Australia, Bristol\\
Miscellaneous& World Cup\\
 Date Expression& 01-02-2012, January, 6th, 1998 \\
Time Expression & 10 p.m.\\
Monetary Value &  \$15, 100 Euro   \\
Percent 30\%&   \\
\end{tabular}
\caption{NE Examples}
\label{table:NETypes}
\end{table}

@@

\subsection*{Issues in Named Entity Recognition}
Among the most common problems for NER is the issue of ambiguity, that is in particular \emph{Polysemy} \cite{ner-sekine2007}, 
the property of some lexical representation having
more than one possible meaning, and \emph{Metonymy}, which refers to the concept of the part-whole/whole-part relation between two expressions. 
\emph{Polysemy} could become an issue for NER when the lexical representation of an item could point to two different \emph{NE} types.
This is quite frequent with \texttt{Person Names} and \texttt{Locations}, since many people are named after cities, such as \emph{Paris} or \emph{Georgia}. 
Often the context will not be disambiguating as in \ref{ex:Paris}.

@@

\subsection*{Methods employed for NER}
For \emph{NER}, there exist both rule-based and statisical approaches. 
Rule-based methods make use of the underlying rules governing languages to extract named entities. 
However, this approach is quite time-consuming and requires extensive work of computational linguists \cite{ner-sekine2007}
and although the results are 
often high in precision, lacks considerably in recall.

In regard to statistical approaches, supervised-learning is the most common method applied in \emph{NER}. Although, there are unsupervised approaches, 
their performance is not as high as for SL applications.

Prominent algorithms in NER include maximum entropy
% Overview algorithms /methods used 
% machine learning/neural networks/rule-based 
% maximum entropy MM
% 
% Base line for NER

@@

@@

\bibliographystyle{acl}
\bibliography{ML}

>>>>

\author{Joachim Daiber \\
  University of Groningen \\
  %Affiliation / Address line 2 \\
  %Affiliation / Address line 3 \\
  {\tt jodaiber@gmx.de} \\\And
  Carmen Klaussner \\
  University of Groningen \\
  %Affiliation / Address line 2 \\
  %Affiliation / Address line 3 \\
  {\tt Carmen@wordsmith.de} \\}

\date{}

@@

\section{Introduction}
Named Entity Recognition (NER) is an information extraction task and has first been introduced as part of the 6th MUC (Sixth Message Understanding Conference)
that was focusing on the extraction of structured information from unstructured text, such as company names from newspaper articles \cite{nadeau2007survey}.
The most prominent types are generally known under the name of \emph{enamex} types, which are comprised of \texttt{Person Names}, \texttt{Organisations} and \texttt{Locations}. 
An additional type \texttt{Miscellaneous} captures person names outside the classic \emph{enamax} type.
Apart from these there is \emph{timex}, which covers date \& time expressions and \emph{numex} which is for monetary values \& percent. 
Table \ref{table:NETypes} gives an overview of the different NE types.

\begin{table}[h!]
\scriptsize
\begin{tabular}{l|l}
\hline
\bf Named Entity Type & \bf Example \\
\hline
Person Names & Greta Garbo, John, Mary \\
Organisations& Benetton, Coca-Cola Gmbh\\
Locations&  Paris, Australia, Bristol\\
Miscellaneous& World Cup\\
 Date Expression& 01-02-2012, January, 6th, 1998 \\
Time Expression & 10 p.m.\\
Monetary Value &  \$15, 100 Euro   \\
Percent &   30\%
\end{tabular}
\caption{NE Examples}
\label{table:NETypes}
\end{table}

@@

\subsection*{Issues in Named Entity Recognition}
Among the most common problems for NER is the issue of ambiguity, that is in particular \emph{Polysemy} \cite{nadeau2007survey}, 
the property of some lexical representation having
more than one possible meaning, and \emph{Metonymy}, which refers to the concept of the part-whole/whole-part relation between two expressions. 
\emph{Polysemy} could become an issue for NER when the lexical representation of an item could point to two different \emph{NE} types.
This is quite frequent with \texttt{Person Names} and \texttt{Locations}, since many people are named after cities, such as \emph{Paris} or \emph{Georgia}. 
Often the context will not be disambiguating as in \ref{ex:Paris}.

@@

\subsection*{Methods employed for NER}
For \emph{NER}, there exist both rule-based and statisical approaches. 
Rule-based methods make use of the underlying rules governing languages to extract named entities. 
However, this approach is high maintenance, quite time-consuming and requires extensive work of computational linguists \cite{nadeau2007survey}
and although the results are 
often high in precision, lacks considerably in recall.

In regard to statistical approaches, supervised-learning is the most common method applied in \emph{NER}. Although, there are unsupervised approaches, 
their performance is not as high as for SL applications yet.

Prominent algorithms in NER include maximum entropy
% Overview algorithms /methods used 
% machine learning/neural networks/rule-based 
% maximum entropy MM
%

\subsection*{CoNLL data set \& baseline}
The training and test dataset was taken from the \emph{CoNLL Shared Task 2002} \cite{TjongKimSang:2003:ICS:1119176.1119195} and the \emph{CoNLL Shared Task 2003} \cite{tksintro2002conll}
for Spanish \& Dutch and English \& German respectively.

% A baseline rate was computed for the English and the
% German test sets. It was produced by a system which
% only identified entities which had a unique class in
% the training data. If a phrase was part of more than
% one entity, the system would select the longest one.
% All systems that participated in the shared task have
% outperformed the baseline system.
% For all the Fβ=1 rates we have estimated sig-
% nificance boundaries by using bootstrap resampling
% (Noreen, 1989). From each output file of a system,
% 250 random samples of sentences have been chosen
% and the distribution of the Fβ=1 rates in these sam-
% ples is assumed to be the distribution of the perfor-
% mance of the system. We assume that performance
% A is significantly different from performance B if A
% is not within the center 90% of the distribution of B.

The baseline for \emph{Named Entity Recognition} in the four different languages is visualised in table \
\begin{table}[h!]
\scriptsize
\begin{tabular}{l|l|l|l}
\hline
\bf Language & \bf Precision & \bf Recall & \bf $F_1$-measure \\ \hline
Spanish &             26.27 \% & 56.48 \% & 35.86  \%        \\
Dutch  &             64.38 \%  &45.19   \%    & 53.10 \%  \\
English &              71.91\%& 50.90 \%  & 59.61 $\pm$ 1.2 \%\\
German &      31.86 \%  & 28.89 \% & 30.30  $\pm$ \%1.3 \\
\end{tabular}
\caption{NER Baseline}
\label{table:Base}
\end{table}

@@

\begin{table}[h!]
\begin{tabular}{l |l| l| l| l| l| l}

\bf Language & \multicolumn{3}{c|}{ \bf testA}&\multicolumn{3}{c}{ \bf testB}\\\hline 
             & Precision & Recall & $F_1$-measure & Precision & Recall & $F_1$-measure \\ \hline
Spanish &       &          &     &          &               & \\
Dutch  &         &          &     &          &               &   \\
English &        &          &     &          &               &       \\
German &      &          &       &          &             & \\
\end{tabular}
\caption{NER Structured Prediction Results }
\label{table:Results}
\end{table}

@@

\bibliographystyle{acl}
\bibliography{paper}
